Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-24 paper.tex
minor fixes

We start by defining a CEK machine \effCEK{C} that is parameterized
over the cast representation $C$
(Section~\ref{sec:framework:cek}). This machine is space efficient
provided that the cast representation performs compression.  The
interface between the machine and the cast representation is defined
by an abstract data type, named Cast ADT, that we define shortly.  We
conjecture that all cast representations defined in the literature
are instances of this ADT.

@@

\begin{definition}[Values and cast results for the \effCEK{C} machine] 
\label{def:values-effCEK}
  \[
  \begin{array}{rclr}
  \stxrule{v}{values}{
    \hcvOOtt \mid
    \hcvOOfun{c}{\rho}{x}{e}{c} \mid
    \hcvOOcons{v}{c}{v}{c} \mid
    \hcvOOinl{v}{c} \mid
    \hcvOOinr{v}{c} \mid
    \hcvOOinj{I}{v}
  }
\stxrule{r}{cast results}{
  \rOOsucc{v} \mid
  \rOOfail{l}
}
  \end{array}
  \]
\end{definition}

\subsection{The Cast Abstract Data Types}

>>>>

We start by defining a CEK machine \effCEK{C} that is parameterized
over the cast representation $C$
(Section~\ref{sec:framework:cek}). This machine is space efficient
provided that the cast representation performs compression.  The
interface between the machine and the cast representation is defined
by an abstract data type, named Cast ADT, that we define shortly 
(Section~\ref{sec:framework:adt}).  We
conjecture that all cast representations defined in the literature
are instances of this ADT.

@@

\begin{definition}[Values and cast results for the \effCEK{C} machine] 
\label{def:values-effCEK}
  \[
  \begin{array}{lrcl}
  \stxrule{v}{Values}{
    \hcvOOtt \mid
    \hcvOOfun{c}{\rho}{x}{e}{c} \mid
    \hcvOOcons{v}{c}{v}{c} \mid
    \hcvOOinl{v}{c} \mid
    \hcvOOinr{v}{c} \mid
    \hcvOOinj{I}{v}
  }
\stxrule{r}{Cast results}{
  \rOOsucc{v} \mid
  \rOOfail{l}
}
  \end{array}
  \]
\end{definition}

\subsection{The Cast Abstract Data Types}
\label{sec:framework:adt}
